
\noindent 
\section{Appendix D: Minutes 01/2/18}

\noindent Meeting Time: 4pm Thursday 25th Jan

\noindent Meeting Location: First Year Labs\textbf{}\\

\noindent 

\noindent \textbf{\underbar{Attendance}}

\noindent Chair: Chong Keat Gea CKG

\noindent Vice-Chair: Kelvin Fang KF

\noindent Secretary: Johnny Allain-Labon JAL

\noindent Treasurer: Mohit Motwani MM

\noindent Georges Ajaka GA

\noindent Course Coordinator Point of Contact: Steven Vuong SV

\noindent Benji Berczi BB

\noindent Alex Stock AS

\noindent 

\noindent Present: CKG KF JAL MM GA SC BB AS

\noindent Absent with Apologies: \\

\noindent 

\begin{enumerate}
\item  \textbf{Overall Group Health CKG}

\begin{enumerate}
\item \textbf{ }Is everyone ok with what they are working on? (People feeling they aren't contributing enough or doing too much etc.)

\item  Any issues wrt group dynamics etc.

\item  Acknowledgement to team sizing issues. Will be discussed again after the updates from each team.

\begin{enumerate}
\item  Going to wait on update from simulation team to rearrange\\
\end{enumerate}
\end{enumerate}

\item  \textbf{Simulation Group Update GA}

\begin{enumerate}
\item \textbf{ }What has been accomplished in the past week? Were the goals set up last week accomplished? (Implement found equations in Java, Meet Monday to update)

\item  Is the GUI working? Yes, CKG to edit

\item  Have the proposed methods been tested / whats the result? None yet - maths still to be implemented

\item  Any issues to raise? (work allocation, number of people,  math etc.)

\item  What's next? Goal setting for next week

\begin{enumerate}
\item  Improve robustness of simulation

\item  Implement and add new maths

\item  Computing power from UCL requires permission from project supervisor\\
\end{enumerate}
\end{enumerate}

\item  \textbf{Prototype Group Update SV}

\begin{enumerate}
\item \textbf{ }What has been accomplished in the past week? Were the goals set up last week accomplished? (Last Week Goals: Fix petri dish to speaker - hot glue? , Decide on oil to use - less viscous, Speaker stand)

\begin{enumerate}
\item  Cameras have been located to use

\item  Demonstrated multiple bouncing drops \& coupling

\item  Tested in f=50-80Hz

\item  Still need to glue base down
\end{enumerate}

\item  Stage of the prototype?

\item  Any issues to raise (work allocation, number of people, what to test next, etc)

\item  What's next? Goal setting for next week

\begin{enumerate}
\item  Glueing base down

\item  Record droplet in motion

\item  Experiment with amplitudes

\item  Quantify observations

\item  Rest tunnelling\\
\end{enumerate}
\end{enumerate}

\item  \textbf{Written Reporting Update MM}

\begin{enumerate}
\item \textbf{ }Where are we on this? Do you need help?

\begin{enumerate}
\item  No progress without maths and finalised equipment list
\end{enumerate}

\item  Has everyone tested the collab?

\begin{enumerate}
\item  JAL can, assume it generalises\\
\end{enumerate}
\end{enumerate}

\item  \textbf{Team reallocation CKG}

\begin{enumerate}
\item \textbf{ }Discussion on needs of each group.

\begin{enumerate}
\item  BB to start work on poster design, collab w MM for copy
\end{enumerate}

\item  Self evaluation on what each person has contributed and areas for improvement.
\end{enumerate}
\end{enumerate}



