
\noindent 
\section{Minutes 18/1/18}\label{app:18-1}

\noindent Meeting Time: 4pm Thursday 18th Jan

\noindent Meeting Location: Massey Group Study Pod, 3rd Floor, Science Library\textbf{}\\

\noindent 

\noindent \textbf{\underbar{Attendance}}

\noindent Chair: Chong Keat Gea CKG

\noindent Vice-Chair: Kelvin Fang KF

\noindent Secretary: Johnny Allain-Labon JAL

\noindent Treasurer: Mohit Motwani MM

\noindent Georges Ajaka GA

\noindent Course Coordinator Point of Contact: Steven Vuong SV

\noindent Benji Berczi BB

\noindent Alex Stock AS

\noindent 

\noindent Present: CKG KF JAL MM GA SV BB AS\\

\noindent 

\begin{enumerate}
\item  \textbf{Simulation Group GA}

\begin{enumerate}
\item How far into the simulation are we?

\begin{enumerate}
\item  3D isn't really possible - only by pre-rendering - takes 5 mins for a pre-rendered version to load

\item  Live-simulation done with heat maps
\end{enumerate}

\item  What can we simulate now?

\begin{enumerate}
\item  Basic animation of wave equation in Python
\end{enumerate}

\item  Have we reached movement?

\begin{enumerate}
\item  Basic movement in Python
\end{enumerate}

\item  Any issues with the coding? 

\begin{enumerate}
\item  Python too slow to render live
\end{enumerate}

\item  Are there sufficient/ too many people working on the code? 

\begin{enumerate}
\item  Don't know yet
\end{enumerate}

\item  Who's done what? Are there any collaboration issues? 

\begin{enumerate}
\item  None yet
\end{enumerate}

\item  Any issues with the code? Buggy, inefficient etc. 

\begin{enumerate}
\item  None to report
\end{enumerate}

\item  What's next? 

\begin{enumerate}
\item  Meeting Monday 11am

\item  Port Python to Java using AWT - JAL

\item  Equations from paper GA AS
\end{enumerate}

\item  Goals setting for next week

\begin{enumerate}
\item  Team GitHub
\end{enumerate}

\item  Who's doing what? 

\item  Discussion with the rest of the team on possible directions and improvements. \\
\end{enumerate}

\item  \textbf{Prototype Group SV}

\begin{enumerate}
\item How far into the prototype are we? 

\begin{enumerate}
\item  Use Veritasium model as baseline

\item  Have list of materials

\item  Pro-level cameras outside our budget $\mathrm{\to}$ use phones with cameras \& timestamps - issues with timing precision
\end{enumerate}

\item  Propose current idea for apparatus

\begin{enumerate}
\item \url{ https://drive.google.com/drive/folders/1OnPH\_cwJg6xc4uVNFHgWOlpQpYrkzFWK}

\item  Total estimated cost $\mathsterling$80
\end{enumerate}

\item  What equipment do we need, how much will it cost us? Budgeting.

\begin{enumerate}
\item  Camera needs depend on aims - do we want to demonstrate (less hi-spec) or do we want to verify theory (higher-spec)

\item  Use IoM for 3D printing, free wood to use in construction

\item  Light diffuser to illuminate surface + drop more softly

\item  Polarising filter to protect camera?
\end{enumerate}

\item  Possible concerns raised with the equipment and discussion on solution. 

\item  Time frame from getting equipment. When will we get everything and start construction?

\begin{enumerate}
\item  3 working days - can pay more for advanced deliver 

\item  Need equipment by Tuesday 23/1
\end{enumerate}

\item  Any task delegation issues, too many/ not enough people. 

\item  What's next? 

\item  Goal setting for next week? 

\item  Whos doing what? 

\item  Discussion with the rest of the team on possible directions and improvements. 

\begin{enumerate}
\item  Derek - Silicone oil given to us.

\begin{enumerate}
\item  He might have a 50W power supply downstairs

\item  Ask about Amazon Packages
\end{enumerate}

\item  To ask Bernard about: 

\begin{enumerate}
\item  Petri Dish (If not, take from Chemistry / Biology)

\item  50W power supply for Subwoofer

\item  3D Printer
\end{enumerate}

\item  Things to Consider: 

\begin{enumerate}
\item  Diffuser: Need a strong lighting source

\item  LEDs?

\item  Powerful lamps perhaps

\item  Polarising Lens perhaps

\item  IoM, check induction times
\end{enumerate}

\item  Creatables: 

\begin{enumerate}
\item  Lab Script for the entire process\\
\end{enumerate}
\end{enumerate}
\end{enumerate}


\noindent 

\item  \textbf{Written Reporting MM}

\begin{enumerate}
\item Minutes from last meeting to ShareLatex

\item  Can start writing theory section now - MM to liaise with GA AS JAL\\
\end{enumerate}

\item  \textbf{Project Management JAL}

\begin{enumerate}
\item Zoho Projects - please confirm login details have been received
\end{enumerate}
\end{enumerate}