\section{Minutes 19/2/18}\label{app:19-2}

\noindent Meeting Time: 11 am Monday 19th Feb 2018

\noindent Meeting Location: Massey Group Study Pod


\noindent \textbf{\underbar{Attendance}}

\noindent Chair: Chong Keat Gea CKG

\noindent Vice-Chair: Kelvin Fang KF

\noindent Secretary: Johnny Allain-Labon JAL

\noindent Treasurer: Mohit Motwani MM

\noindent Georges Ajaka GA

\noindent Course Coordinator Point of Contact: Steven Vuong SV

\noindent Benji Berczi BB

\noindent Alex Stock AS

\noindent 

\noindent Present: CKG KF JAL MM GA SC BB AS

\noindent Absent with Apologies: 



\begin{enumerate}
\item  \textbf{Overall Group Health CKG}

\begin{enumerate}
\item Is everyone ok with what they are working on? (People feeling they aren't contributing enough or doing too much etc.)

\item  Any issues wrt group dynamics etc.

\end{enumerate}

\item  \textbf{Simulation Group Update GA}

\begin{enumerate}
\item What has been accomplished in the past week? Were the goals set up last week accomplished?

\begin{enumerate}
\item  Matlab: GUI working but generating data is inefficient + only marginal optimisation feasible

\item  Java: calculations much more efficient but GUI is the bottleneck
\end{enumerate}

\item  Any issues to raise? (work allocation, number of people,  math etc.)

\item  What's next? Goal setting for next week

\begin{enumerate}
\item  Connect Matlab to Java to get best of both worlds - call out to shell https://uk.mathworks.com/help/matlab/matlab\_external/run-external-commands-scripts-and-programs.html?s\_tid=gn\_loc\_drop

\item  Investigate alternative plotting methods in Java sim. to Matplotlib

\item  Investigate pre-generating data - although defeats purpose of live simulation

\item  Unlikely to be able to generate live GUI $\mathrm{\to}$ restrict to generating videos
\end{enumerate}

\end{enumerate}

\item  \textbf{Prototype Group Update SV}

\begin{enumerate}
\item What has been accomplished in the past week? Were the goals set up last week accomplished?

\begin{enumerate}
\item  Meeting with education dept. of Physics

\item  Developed lesson plan to plan school visit as trial - can be simplified - JAL to edit
\end{enumerate}

\item  Stage of the prototype?

\begin{enumerate}
\item  Wed 21/2 using high-speed camera

\item  Want to continue testing tracking of motion with a camera and AfterEffects
\end{enumerate}

\item  Any issues to raise (work allocation, number of people, what to test next, etc)

\item  What's next? Goal setting for next week

\begin{enumerate}
\item  Education - meeting with Mark to discuss lesson plan (JAL \& MM), JAL to email Highgate school

\item  Difficult to get quantifiable data from simulation
\end{enumerate}

\end{enumerate}

\item  \textbf{Written Reporting Update MM}

\begin{enumerate}
\item Added more to apparatus list - need input from prototype group

\item  Education stuff to be added

\item  All teams need to start writing now

\item  Need timeline for report - deadline for the 11th March for all work submission

\item  Paying for ShareLatex subscription - add $\mathsterling$7.20 to the budget
\end{enumerate}

\item  \textbf{Group report submission}

\begin{enumerate}
\item Report to be submitted by Wednesday, approved by group

\item  Need to clarify who it needs to be sent to
\end{enumerate}
\end{enumerate}

