\noindent 
\section{Minutes 25/1/18}\label{app:25-1}

\noindent Meeting Time: 4pm Thursday 25th Jan

\noindent Meeting Location: Group Study Pod 3, Ground Floor, Science Library\textbf{}\\

\noindent 

\noindent \textbf{\underbar{Attendance}}

\noindent Chair: Chong Keat Gea CKG

\noindent Vice-Chair: Kelvin Fang KF

\noindent Secretary: Johnny Allain-Labon JAL

\noindent Treasurer: Mohit Motwani MM

\noindent Georges Ajaka GA

\noindent Course Coordinator Point of Contact: Steven Vuong SV

\noindent Benji Berczi BB

\noindent Alex Stock AS

\noindent Prof Ryan Nichol RN

\noindent 

\noindent Present: CKG KF JAL MM GA SV BB AS

\noindent Absent with Apologies: RN\\

\noindent 

\begin{enumerate}
\item  \textbf{Overall Group Health CKG}

\begin{enumerate}
\item Is everyone ok with what they are working on? (People feeling they aren't contributing enough or doing too much etc.)

\item  Any issues wrt group dynamics etc? No, all going OK.

\end{enumerate}

\item  \textbf{Simulation Group Update GA}

\begin{enumerate}
\item What has been accomplished in the past week? Were the goals set up last week accomplished? (Last Week Goals: Team github)

\begin{enumerate}
\item  Github permissions are tricky
\end{enumerate}

\item  Request for help: equations to implement in code

\begin{enumerate}
\item  Possible solution would be to square the wave to generate probability of next position and velocity towards next position can be calculated using time stamp (CKG)

\item  GUI written but not running yet - error on compilation

\item  AS - update on equations - need to do integrals by brute force but should work - possibly computationally intensive? And has expected values of coefficients - \url{http://dx.doi.org/10.1063/1.4817612} \url{https://www.cambridge.org/core/journals/journal-of-fluid-mechanics/article/drops-bouncing-on-a-vibrating-bath/441A614F657E800EA06F6C08674CCE67}
\end{enumerate}

\item  Discussion on possible solution

\item  What's next, who does what?

\begin{enumerate}
\item  Implement found equations in Java

\item  Meet Monday to update
\end{enumerate}

\item  Someone to join simulation team eventually?\\
\end{enumerate}

\item  \textbf{Prototype Group Update SV}

\begin{enumerate}
\item What has been accomplished in the past week? Were the goals set up last week accomplished? (Last Week Goals: ??)

\begin{enumerate}
\item  Got prototype working but droplets too large - due to viscosity? Use different oil with lower viscosity

\item  Smaller droplets accomplished by using a finer point, or using a device to release the drop at a given time
\end{enumerate}

\item  Discussion on the different proposed apparatus. To glue or not to glue?

\begin{enumerate}
\item  Attempt non-permanent options before gluing - double sided tape, 
\end{enumerate}

\item  Any more equipment need purchasing?

\begin{enumerate}
\item  Need to look at other amps - EEng?
\end{enumerate}

\item  What's next, who does what?

\begin{enumerate}
\item  Next Weds for labs

\item  Fix petri dish to speaker - hot glue?

\item  Decide on oil to use - less viscous - CK \& BB

\item  Speaker stand - CK\\
\end{enumerate}
\end{enumerate}

\item  \textbf{Written Reporting Update MM}

\begin{enumerate}
\item Where are we on this? Do you need help? 

\begin{enumerate}
\item  ShareLatex set up - everyone to test collaboration access please\\
\end{enumerate}
\end{enumerate}

\item  \textbf{AOB}

\begin{enumerate}
\item Speakers - driven by a signal generator

\item  Can purchase an amplifier if needed - money available in budget - $\mathsterling$125 left
\end{enumerate}
\end{enumerate}




