\section{Minutes 27/2/18} \label{app:27-2}

\noindent Meeting Time: 10 am Tuesday 27th Feb 2018

\noindent Meeting Location: Study Pod 3, SciLib Ground Floor



\noindent \textbf{\underbar{Attendance}}

\noindent Chair: Chong Keat Gea CKG

\noindent Vice-Chair: Kelvin Fang KF

\noindent Secretary: Johnny Allain-Labon JAL

\noindent Treasurer: Mohit Motwani MM

\noindent Georges Ajaka GA

\noindent Course Coordinator Point of Contact: Steven Vuong SV

\noindent Benji Berczi BB

\noindent Alex Stock AS

\noindent Prof Ryan Nichol RN

\noindent 

\noindent Present: KF JAL MM SC BB RN CKG

\noindent Absent with Apologies: GA

\noindent Absent without Apologies: AS



\begin{enumerate}
\item  \textbf{Overall Group Health CKG}

\begin{enumerate}
\item Is everyone ok with what they are working on? (People feeling they aren't contributing enough or doing too much etc.)

\item  Any issues wrt group dynamics etc.
\vspace{5mm}

\end{enumerate}

\item  \textbf{Simulation Group Update GA}

\begin{enumerate}
\item What has been accomplished in the past week? Were the goals set up last week accomplished?

\begin{enumerate}
\item  Matlab: Wave decays over time. Not working for bouncing droplet. Difficult to store all past waves as too much data

\item  Java: calculations much more efficient but GUI is the bottleneck. Amplitude is constant to begin with. Wave does not decay, perpetuates itself. Bouncing droplet has upper limit for velocity. Particle interacts with surface and goes into - not meant to happen
\end{enumerate}

\item  Any issues to raise? (work allocation, number of people,  math etc.)

\begin{enumerate}
\item  Model is too complex? Perhaps try to simplify to one wave
\end{enumerate}

\item  What's next? Goal setting for next week

\begin{enumerate}
\item  Leaving simulation here - too difficult to improve computation significantly

\item  Will attempt to port Matlab to Java

\item  Will look into pre-generating data and replaying that in the simulation
\end{enumerate}
\vspace{5mm}

\end{enumerate}

\item  \textbf{Prototype Group Update SV}

\begin{enumerate}
\item Education group update?

\begin{enumerate}
\item  Met with Phys education outreach officer

\item  Have arranged 1 hour demo at MM's old school - to take place on Weds 7/3 - JAL MM \& SV - meet UCL Lab 3 @ 9:30am \& meet Thurs 1/3 4pm to plan
\end{enumerate}

\item  Stage of the prototype?

\begin{enumerate}
\item  Wed 21/2 using high-speed camera - successful, can see waves with naked eye \url{https://drive.google.com/open?id=13hn0rVRsYw901Yoh2cBnKkRr2TJnk2Du}

\item  Want to continue testing tracking of motion with a camera and AfterEffects - haven't attempted but can process video this week
\end{enumerate}

\item  Any issues to raise (work allocation, number of people, what to test next, etc)

\item  What's next? Goal setting for next week

\begin{enumerate}
\item  Writing proposal to STFC for public engagement funding - BB

\item  SV \& KF to write up prototype process

\item  Paint \& decorate prototype - B R A N D I N G
\end{enumerate}
\vspace{5mm}

\end{enumerate}

\item  \textbf{Written Reporting Update MM}

\begin{enumerate}
\item JAL has written up some of computing

\item  No major updates from MM

\item  Uncertain how our project will demonstrate quantum effects
\vspace{5mm}
\end{enumerate}

\item  \textbf{Poster JAL}

\begin{enumerate}
\item JAL to edit
\vspace{5mm}
\end{enumerate}

\item  \textbf{Next meeting 8/3/18 4pm}
\end{enumerate}

