\section{Minutes 08/2/18}\label{app:8-2}

\noindent Meeting Time: 4pm Thursday 8th Feb 2018

\noindent Meeting Location: Sci Lib Study Pod 2\textbf{}



\noindent \textbf{\underbar{Attendance}}

\noindent Chair: Chong Keat Gea CKG

\noindent Vice-Chair: Kelvin Fang KF

\noindent Secretary: Johnny Allain-Labon JAL

\noindent Treasurer: Mohit Motwani MM

\noindent Georges Ajaka GA

\noindent Course Coordinator Point of Contact: Steven Vuong SV

\noindent Assessor of Group 14: Benji Berczi BB

\noindent Alex Stock AS

\noindent Prof Ryan Nichols RN

\noindent Javier Gomez de la Gandara JGG

\noindent Gordon Qiu GQ

\noindent 

\noindent 

\noindent Present: CKG KF JAL MM GA SV AS

\noindent Absent with Apologies: BB

\noindent Absent without Apologies: RN



\begin{enumerate}
\item  \textbf{Overall Group Health CKG}

\begin{enumerate}
\item Is everyone ok with what they are working on? (People feeling they aren't contributing enough or doing too much etc.)

\begin{enumerate}
\item  JAL to switch to poster design + help MM with report
\end{enumerate}

\item  Any issues wrt group dynamics etc.

\item  Reminder on goals to be accomplished by reading week (12/2 - READING WEEK - Basic simulation + prototype completed)

\item  Reminder of future goals:

\begin{enumerate}
\item  Reading Week - report to other group - done to be finalised

\item  7/3 - prelim deadline for poster being finalised for printing

\item  16/3 5pm - FINAL REPORT due + critical self-assessment

\item  21/3 - poster presentation
\end{enumerate}


\end{enumerate}

\item  \textbf{Simulation Group Update GA}

\begin{enumerate}
\item What has been accomplished in the past week? Were the goals set up last week accomplished? (Improve robustness of simulation, Implement and add new maths, Computing power from UCL requires permission from project supervisor)

\begin{enumerate}
\item  Issues with lack of computing power to run simulation efficiently

\item  Need to email ISD about access to computing power - GA
\end{enumerate}

\item  Issues with current GUI.

\begin{enumerate}
\item  Lines are working now

\item  Speed to be optimised
\end{enumerate}

\item  Math implementation

\begin{enumerate}
\item  Lorentz transform results in imaginary numbers which is not real

\item  To discuss with RN

\item  AS has generation of position and wavefield at every point but takes two seconds to generate
\end{enumerate}

\item  Any issues to raise? (work allocation, number of people,  math etc.)

\item  Review of goals set to be accomplished by reading week (basic simulation?)

\begin{enumerate}
\item  Not quite but close - might be basic errors. Need to decide between AS and CKG's simulations. To be chosen 9/2
\end{enumerate}

\item  What's next? Goal setting for w/c 19/2

\begin{enumerate}
\item  Need working simulation - hopefully within a few days

\item  Interactivity - easy extension of current system

\item  Unify codebase to give one working prototype

\item  Switch primary aim to demonstrate quantum effects - but will depend on success of basic simulation.
\end{enumerate}

\end{enumerate}

\item  \textbf{Prototype Group Update SV+KF}

\begin{enumerate}
\item What has been accomplished in the past week? Were the goals set up last week accomplished? (Last Week Goals: Glueing base down, Record droplet in motion, Experiment with amplitudes, Quantify observations, Rest tunnelling)

\begin{enumerate}
\item  Issue with camera prevented recording

\item  Splitting group into two:

\begin{enumerate}
\item  MM \& BB - education outreach \& commercialisation. Currently in emailing stage. Apparatus might need to be simplified e.g. no amplifier, different oils - to be isolated and tested. Ask about outreaching with UCAS offer holders

\item  SV \& KF - developing the experiment. Likely walking droplets, orbiting droplets and standing waves are possible. 9/2/18 recording with high-speed camera to be attempted. Unlikely to achieve quantum effects $\mathrm{\to}$ ideally occur within the simulation.
\end{enumerate}
\end{enumerate}

\item  Stage of the prototype? (formed sub-groups within prototype group)

\item  Any issues to raise (work allocation, number of people, what to test next, etc)

\begin{enumerate}
\item  Difficult to produce diffraction

\item  Want to minimise number of independent variables where possible i.e. restrict to just frequency

\item  Difficult to make droplets of a consistent size - want to measure using camera/graph paper
\end{enumerate}

\item  Review of goals set to be accomplished by reading week (prototype completed?)

\begin{enumerate}
\item  Demonstrates stable bouncing and wave-like behaviour
\end{enumerate}

\item  What's next? (recording this Friday at 12-2)

\item  Goal setting for next week (SV and KF collecting data during reading week)

\begin{enumerate}
\item  Want education team to go as far as possible

\item  Changes to air pressure to manipulate droplet's movement and force through a barrier

\item  Not sure of scale of education outreach possible - looking for feedback from schools as to this

\item  Recut box to include amplifier

\item  Group to meet at some point in reading week
\end{enumerate}

\end{enumerate}

\item  \textbf{Written Reporting Update MM}

\begin{enumerate}
\item Where are we on this? Do you need help?

\begin{enumerate}
\item  Some justification and detail has been added i.e. why we're making the design choices we do

\item  Photography of apparatus would be useful

\item  JAL to edit write up
\end{enumerate}

\end{enumerate}

\item  \textbf{Assessment of Group 14 BB \& AS}

\begin{enumerate}
\item What was the group's performance like

\item  Everyone's view on the document prepared by BB

\item  When to finalize? (group 14 was asking for our assessment write up) JAL to edit + review then approve on group chat

\end{enumerate}

\item  \textbf{Questions for External Reviewers GQ JGG}

\begin{enumerate}
\item Any differences to be made looking back?

\begin{enumerate}
\item  Define proper timeline - to be done 

\end{enumerate}

\item  BB Absence?

\begin{enumerate}
\item  Flying home for reading week
\end{enumerate}

\item  Task management?

\begin{enumerate}
\item  Done via agendas + group chats
\end{enumerate}

\item  Challenges?

\begin{enumerate}
\item  Sourcing equipment - help from Engineering, Derick

\item  Liquid viscosity - had to source from elsewhere

\item  Efficiency of computation with simulation

\item  Collaborative coding

\item  Understanding of maths
\end{enumerate}

\end{enumerate}

\item  \textbf{Next meeting?}

\begin{enumerate}
\item During reading week or after reading week?

\begin{enumerate}
\item  Monday 11am 19/2

\item  MM SV KF Meeting 9/2 11:30
\end{enumerate}

\item  What to be accomplished by then?

\item  Start on posters (who are more suitable?)

\begin{enumerate}
\item  JAL to lead
\end{enumerate}
\end{enumerate}
\end{enumerate}

\noindent 