\noindent 
\section{Minutes 08/03/18}\label{app:8-3}

\noindent Meeting Time: 4 pm Thursday 8th Mar 2018

\noindent Meeting Location: Engineering Study room, DMS Watson


\noindent \textbf{\underbar{Attendance}}

\noindent Chair: Chong Keat Gea CKG

\noindent Vice-Chair: Kelvin Fang KF

\noindent Secretary: Johnny Allain-Labon JAL

\noindent Treasurer: Mohit Motwani MM

\noindent Georges Ajaka GA

\noindent Course Coordinator Point of Contact: Steven Vuong SV

\noindent Benji Berczi BB

\noindent Alex Stock AS

\noindent Prof Ryan Nichol RN

\noindent 

\noindent Present: CKG KF JAL MM GA SV BB AS RN

\noindent Absent with Apologies: 

\noindent Absent without Apologies: 



\begin{enumerate}
\item  \textbf{Overall Group Health CKG}

\begin{enumerate}
\item Is everyone ok with what they are working on? (People feeling they aren't contributing enough or doing too much etc.)

\item  Any issues wrt group dynamics etc - no

\item  Quick update on due dates

\begin{enumerate}
\item  7/3 - prelim deadline for poster being finalised for printing (LATE) delayed due to formal report and pushing boundaries on experiment. 

\item  16/3 5pm - FINAL REPORT due + critical self-assessment
\end{enumerate}

\end{enumerate}

\item  \textbf{Written Reporting Update MM}

\begin{enumerate}
\item The current overall structure of the written report. What goes where?

\item  Help needed from each section. 

\item  What is needed in the appendix $\mathrm{\to}$ all code written for simulation? All schematics used to produce the prototype? Correspondence? Minutes? Confirm with Ryan what he wants in here.

\end{enumerate}

\item  \textbf{Simulation Group Update GA}

\begin{enumerate}
\item What has been accomplished in the past week? Were the goals set up last week accomplished? (Last weeks goals: Leaving simulation here - too difficult to improve computation significantly, Will attempt to port Matlab to Java, Will look into pre-generating data and replaying that in the simulation) Yes all complete.

\item  Closing discussion on simulation - no more progress from this point on. focus on report. Give a summary on what has been accomplished from start to end.

\item  Written report section progress - the plan on how this section will be structured.

\end{enumerate}

\item  \textbf{Prototype Group Update SV}

\begin{enumerate}
\item Education group update? How did the trip to the school go? Went well, positive feedback in reviews and from teacher.

\item  Stage of prototype and what has been accomplished over the past week.

\item  Closing discussion on prototype - no more progress from this point on.  Focus on report. Give summary on what has been accomplished from start to end.

\item  Written report section progress - the plan on how this section will be structured.
\end{enumerate}


\item  \textbf{Poster JAL}

\begin{enumerate}
\item Delayed due to formal report. 

\item  How we plan to structure it  $\mathrm{\to}$ what diagrams do we want in here.  
\end{enumerate}

\end{enumerate}


